### 2016-11-02 paper/intro.tex
pass on intro and modes

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both elements can add up on the
aggregate cost of running a test suite, leading to late reports of test
failures, which can disrupt the development
process~\cite{hilton-etal-ase2016}.  This is often referred to as the
``regression testing problem''.  At large IT companies (e.g.,
Groupon~\cite{kim-etal-fse2013}), dealing with high testing costs is a
common problem .  \Mar{Ask Milos if he can share stories on how
  prevalent regression testing is at Microsoft and Google, if he can
  explain how they run tests, and how prevalent is parallelization (in
  contrast to regression testing).}

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
unsound (\ie{}, they do not guarantee that fault-revealing tests will
be selected), however, more recently, sound techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
example, to soundly select tests for execution,
Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} analyzes which files
that a given test depends on have been impacted by changes. File
dependencies are computed and maintained at low cost.

Although regression testing is a recognized problem in academia and at
large IT organizations, to the best of our knowledge no prior work has
investigated how prevalent the problem is in open-source projects.  We
understand that the alternative of renting server farms (or even
building one) to mitigate the regression testing problem is a
potential escape for large IT organizations but not as attractive for
open-source projects and projects from smaller organizations with
lower budgets for building testing infrastructures.  This paper
studies (1) how relevant the problem of long-running test suites in
open-source software is, (2) what are the causes of high execution
cost (CPU vs. IO), and (3) what is the impact of existing open-source
sound approaches to reducing cost.

@@

Given the proliferation of multicore machines it is not surprising
that popular build systems and testing frameworks provide today
support for parallel test execution with the goal of running tests
more efficiently~\cite{junit-org,testng,nunit,maven-surefire-plugin}.
The lower-level parallelism enabled through build systems and testing
frameworks is an important complement to the higher-level parallelism
enabled through server farms.  These solutions enable the use of
commodity hardware to maximize CPU usage\footnote{In the case of the
Java language, for example, it is possible to explore parallelism
across and within JVMs.}.  For the scenario of large IT organizations,
lower-level parallelization schemes could leverage the computing power
of server nodes in addition to the aggregate processing power of the
farm.  Lower-level parallelism fits particularly well smaller
organizations (/projects) with relatively high testing costs but lower
budgets.  \Comment{Unfortunately, these solutions can't be used out-of-the-box:
unrestricted parallel execution of tests can produce non-deterministic
results as developers typically do not provision protection to
concurrent accesses originated from arbitrary program points (\ie{},
tests).  We refer to this problem as Parallel Execution Flakiness
(\pef{}).}

@@

\Comment{
To illustrate the importance of parallel test execution and
the problem of \pef{} let's consider the case of the ``core'' module
from the Apache Camel project~\cite{apache-camel-web}.  This module
contains 5,679 test cases, declared in 2,356 test classes.  We ran
those tests in a machine with 16GB of memory and 8 virtual CPUs (4
cores with 2 native threads each).  Sequential test execution takes
24m50s to run this test set.  Execution of the same test set takes
2m28s when we configured parallel execution to fork a JVM per CPU and
execute test classes, uniquely allocated to that JVM, sequentially but
running test methods from each class in separate threads.  Note that
this is an order of magnitude speedup (10.07x)\Fix{Need to understand
why this is 10x as opposed to something closer to 7x - I didn't get
your concern here}.  Unfortunately, due to \pef{}, $\sim$2\% (114 of
5,679) of the tests fail when executed in parallel.  It is important
to notice that the ratio of failures varies with the project as it
depends on factors such as length of test cases and amount of shared
state across tests.

\pef{} is an important obstacle to enable parallel test execution.
Conceptually, higher parallelization can result in higher chances of
concurrency-related problems.  It is important to execute tests
efficiently without sacrificing reliability
\Fix{gap between pars?? What gap?}

}

@@

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
%%  LocalWords:  Ekstazi

>>>>

%% . which can disrupt the development
%% process~\cite{hilton-etal-ase2016}.\Comment{  This is often referred to as the
%% ``regression testing problem''.}

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both elements can add up to the
aggregate cost of running a test suite, which can lead to late reports of test
failures.  At large IT companies (e.g.,
Groupon~\cite{kim-etal-fse2013}), dealing with high testing costs is a
common problem .  \Mar{Ask Milos if he can share stories on how
  prevalent regression testing is at Microsoft and Google, if he can
  explain how they run tests, and how prevalent is parallelization (in
  contrast to regression testing).}

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Most of these techniques are
unsound (\ie{}, they do not guarantee that fault-revealing tests will
be selected), however, more recently, sound techniques have been
proposed~\cite{gligoric-etal-issta2015,soetens-etal-2016}.  For
example, to soundly select tests for execution,
Ekstazi\cite{ekstazi-web,gligoric-etal-issta2015} conservatively
computes which tests have been impacted by changes.  It analyzes, for
each test, which file dependencies have been change impacted.

%; these
%dependencies are computed and maintained at low cost.

Although regression testing is a recognized problem in academia and at
large IT organizations, to the best of our knowledge no prior work has
investigated how prevalent the problem is in open-source projects.
For large IT organizations, the alternative of renting server farms,
or even building one, is a potential escape to the regression testing
problem.  However, for open-source projects and for projects of
smaller organizations with lower budgets for building testing
infrastructures, this alternative may not be as attractive.

\newcommand{\numSubjs}{143}

Motivated by this potential gap in regression testing practice, this
paper studies (1) how prevalent long-running test suites are in
open-source software projects.  To conduct this experiment we selected
\numSubjs{} Java projects from github that are highly-popular and use
the Maven build system.  (Section~\ref{sec:eval} details our selection
criteria.)  Our experimental results indicate that long-running test
suites (taking longer than 5m\Fix{check if Ekstazi paper also used
  this value and cite} to complete) are not rare (\Fix{17\%} of the
projects).  From this result we investigated (2) how frequently
long-running test suites use parallelization.  Our results indicate
that \Fix{80\%} of the long-running projects do use parallelization to
speedup execution.  Given the popularity of this solution, we further
studied: (3) what are the causes of high execution cost in individual
tests (CPU vs. IO) and (4) how uniformly cost is distributed across
tests.  These questions help to assess the impact of parallelization
in each of these projects.  Intuitively, IO-intensive test suites and
test suites with uneven distribution of cost per test are factors that
limit the effects of parallelization.  Results indicate that \Fix{...}
Finally, we investigated (5) what are the limitations related with
parallelization that could justify adoption resistance.

@@

@@

@@

%%  LocalWords:  parallelization multicore JUnit TestNG NUnit XXm YYm
%%  LocalWords:  Groupon parallelizing multi JVMs CPUs JVM Milos TODO
%%  LocalWords:  Ekstazi github

### 2016-11-02 paper/modes.tex
pass on intro and modes

Parallelism in test execution can be achieved at different levels.
Figure~\ref{fig:levels} illustrates that.\Fix{...}  This paper focuses
at lower-level parallelism that can be achieved through build systems
and testing frameworks.  In the following we elaborate relevant
features of these components focusing on Java, Maven, and JUnit but
the discussion can be generalized to other languages, build systems,
and testing frameworks.

>>>>

%%, potentially using commodity hardware

Parallelism in test execution can be obtained at different levels.
Figure~\ref{fig:levels} illustrates some of these levels.  This paper
focuses at lower-level parallelism, obtained with parallel computation
at cpus and threads in a given machine.  This kind of parallelism is
enabled through build systems and testing frameworks.  Given the
proliferation of multicore machines it is not surprising that testing
frameworks provide today support for parallel test execution with the
goal of running tests more efficiently~\cite{junit-org,testng,nunit}.
Build systems wrap the features of these frameworks to facilitate the
use of such technology\cite{maven-surefire-plugin}.  In the following
we elaborate relevant features of these components focusing on Java,
Maven, and JUnit but the discussion can be generalized to other
languages, build systems, and testing frameworks.

Note that lower-level parallelism is a complement to higher-level
parallelism that could be enabled through server farms.  For the
scenario of large IT organizations, lower-level parallelization
schemes could leverage the computing power of server nodes in addition
to the aggregate processing power of the farm.  Lower-level
parallelism fits particularly well smaller organizations (/projects)
with relatively high testing costs but lower budgets.
\Comment{Unfortunately, these solutions can't be used out-of-the-box:
  unrestricted parallel execution of tests can produce
  non-deterministic results as developers typically do not provision
  protection to concurrent accesses originated from arbitrary program
  points (\ie{}, tests).  We refer to this problem as Parallel
  Execution Flakiness (\pef{}).}

%% These solutions enable the
%% use of commodity hardware to maximize CPU usage\footnote{In the case
%%   of the Java language, for example, it is possible to explore
%%   parallelism across and within JVMs.}.

\Comment{
To illustrate the importance of parallel test execution and
the problem of \pef{} let's consider the case of the ``core'' module
from the Apache Camel project~\cite{apache-camel-web}.  This module
contains 5,679 test cases, declared in 2,356 test classes.  We ran
those tests in a machine with 16GB of memory and 8 virtual CPUs (4
cores with 2 native threads each).  Sequential test execution takes
24m50s to run this test set.  Execution of the same test set takes
2m28s when we configured parallel execution to fork a JVM per CPU and
execute test classes, uniquely allocated to that JVM, sequentially but
running test methods from each class in separate threads.  Note that
this is an order of magnitude speedup (10.07x)\Fix{Need to understand
why this is 10x as opposed to something closer to 7x - I didn't get
your concern here}.  Unfortunately, due to \pef{}, $\sim$2\% (114 of
5,679) of the tests fail when executed in parallel.  It is important
to notice that the ratio of failures varies with the project as it
depends on factors such as length of test cases and amount of shared
state across tests.

\pef{} is an important obstacle to enable parallel test execution.
Conceptually, higher parallelization can result in higher chances of
concurrency-related problems.  It is important to execute tests
efficiently without sacrificing reliability
\Fix{gap between pars?? What gap?}

}
